Vulnerability Analysis of Container Images in Neuroimaging

### 2020-09-01 paper.tex
More updates in abstract

\begin{abstract}
Software containers have become key technologies for the deployment of
scientific data analyses on high-performance computing (HPC)
infrastructures. They facilitate analysis portability, deployment, and
reproducibility. Container images, however, often contain slightly outdated
software packages compared to HPC environments maintained by professional
and dedicated system administrators. In addition, they often carry more
software packages than required by analyses, including compilers or unused
system librairies. As a result, container images are likely to contain
important amounts of security vulnerability, increasing the attack surface
for the entire infrastructure. This paper presents a vulnerability analysis
of container images for scientific data analysis. We analyze container
images with four vulnerability scanners, focusing on the use case of
neuroscience data analyses. We quantify the effect of images updates and
size reduction on the number of vulnerabilities, and conclude with
recommendations on how to build container images with a reduced amount of
vulnerabilities.

>>>>

\begin{abstract}
Software containers have become key technologies for the deployment of
scientific data analyses on high-performance computing (HPC)
infrastructures, due to their positive impact on the portability, deployment, and
reproducibility of computations. Container images, however, often contain slightly outdated
software packages compared to HPC environments maintained by professional
 system administrators, and they often carry more
software packages than required by analyses, including compilers or unused
system librairies. As a result, container images are likely to contain
important amounts of security vulnerability, increasing the attack surface
for the entire infrastructure. This paper presents a vulnerability analysis
of container images for scientific data analysis. We analyze container
images with four vulnerability scanners, focusing on the use case of
neuroscience data analyses. We quantify the effect of images updates and
size reduction on the number of vulnerabilities, and conclude with
recommendations on how to build container images with a reduced amount of
vulnerabilities.
